\cvsection{Works}

\cvsubsection{Open Source Projects}

\begin{cventries}
  \cvcompactentry
    {V programming language - Definition and Interpreter.}
    {V Language}
    {\href{https://github.com/AvatarHurden/V}{GitHub}}
    {2016}
  \cvcompactentry
    {Python plugin to convert currencies in Keypirinha (Keyboard Launcher for Windows).}
    {Keypirinha Currency}
    {\href{https://github.com/AvatarHurden/keypirinha-currency}{GitHub}}
    {2017}
  \cvcompactentry
    {A journaling application made in Java.}
    {DayByDay}
    {\href{https://github.com/AvatarHurden/DayByDay}{GitHub}}
    {2015}
% \cvcompactentry
%   {BH Tree-based N-body simulator in Java with a space theme.}
%   {Galaxy Simulator}
%   {\href{https://github.com/AvatarHurden/Simulador-Galaxias}{GitHub}}
%   {2016}
% \cvcompactentry
%   {Visual application for finding Cliques and Independent Sets in arbitraty graphs}
%   {Clique and Independent Set Calculator}
%   {\href{https://github.com/AvatarHurden/Clique-and-Ind.Set-Calculator}{GitHub}}
%   {2014}

\end{cventries}

\newpage

\cvsubsection{Papers}

\begin{cventries}
  \cventry
    {\href{http://seer.ufrgs.br/rita/article/view/VOL25_NR3_89}{RITA Vol 25, No 3 - pp. 89-101}}
    {V: a language with extensible record accessors and a trait-based type system}
    {2018}
    {}
    {
      \begin{cvitems}
        \item {Reduced version published in \href{http://weit2017.inf.ufsm.br/wp-content/uploads/2017/10/Versao_final.pdf}{WEIT 2017 Annals - pp. 294-301}}.
      \end{cvitems}
    }
\end{cventries}

\cvsubsection{iOS Apps}

\begin{cventries}
  \cvcompactentry
    {An iOS/watchOS app with journaling and a breathing exercise to help with anxiety or panic attacks.}
    {Breather}
    {\href{https://itunes.apple.com/app/id1370659046?mt=8}{App Store}}
    {2018}
  \cvcompactentry
    {Multi-user iOS and tvOS app to create business model canvases.}
    {Business Canvas TV}
    {\href{https://itunes.apple.com/app/id1292335686?mt=8}{App Store}}
    {2017}
  \cvcompactentry
    {A beat'em up rhythm game in the style of 80's zombies.}
    {Rhythm'Em Up}
    {\href{https://itunes.apple.com/app/id1262013610?mt=8}{App Store}}
    {2017}
  \cvcompactentry
    {A game where you play Brazil's unpopular president, Temer, trying to escape from riots.}
    {Fora Memer}
    {\href{https://itunes.apple.com/br/app/fora-memer/id1253655537?l=en&mt=8}{App Store}}
    {2017}
  \cvcompactentry
    {Educational app to teach basic and compound interest.}
    {EduFin}
    {\href{https://itunes.apple.com/app/id1231577657?mt=8}{App Store}}
    {2017}
\end{cventries}

% \begin{cventries}
%   \cventry
%     {}
%     {Business Canvas TV}
%     {App Store}
%     {2017}
%     {}
%   \cventry
%     {}
%     {}
%     {App Store}
%     {2017}
%     {}
%   \cventry
%     {}
%     {}
%     {App Store}
%     {2017}
%     {}
% \end{cventries}
