%<*data>
\recipientname{Scott Logic}

\letterdate{\today}
\lettertitle{Graduate Software Developer}
\letteropening{Dear HR Team,}
\letterclosing{Looking forward to hearing from you.\\
\\
Sincerely,}
%</data>

%<*content>
\cvparagraph{About Me}

I am a Computer Science Undergraduate student graduating at the end of this year.
I have also been a student at the Apple Developer Academy for almost 2 years, during which time I have developed and published more than 5 iOS apps.
I currently live in Brazil, but I am an Italian citizen looking to move to the UK to start my career.
Having been in academia for almost 5 years (the usual length of undergraduate courses in Brazil), I am looking to find jobs where I can use what I have learned in real-world scenarios.

\cvparagraph{Why Scott Logic?}

The Graduate Software Developer position offered by Scott Logic is ideal for me for many reasons.
The first is that I would be able to learn real-world applications of the abstract knowledge I have gained during my undergraduate programme, solving problems that are large both in terms of complexity and scale.
Furthermore, creating applications that serve the needs of actual people is an extremely rewarding task, as I have learned when making iOS applications.

Working with many different technologies is something that I always look forward to, and the promise of participating in the development of web, mobile and desktop applications is highly attractive.
Working in an agile-oriented cross-discpline team of developers, designers and testers creates a challenging and dynamic environment and one in which I would certainly excel.

\cvparagraph{Why Me?}

I have a very strong background in data structures and algorithms, built upon the foundations that I received from my undergraduate programme.
This gives me the ability to quickly see bottlenecks and areas in which efficiency (both in terms of storage and speed) can be improved.
Furthermore, I have almost 2 years of experience developing iOS applications with an Agile approach, which has given me experience in understanding the actual needs of users and delivering products that fulfil those needs.

My work has been recognized both in academia and industry, such as by winning a Student Scholarship to Apple's WWDC, publishing an article in an academic journal and placing second in a regional programming marathon.
Given my proven experience in theoretical computer science and practical application development, I believe I would be a great fit for the Graduate Software Developer position.
%</content>
